---
title: "Schedule"
description: |
  Schedule for Math 150, Methods in Biostatistics, Spring 2023
execute: 
  message: false
  warning: false
---

```{r}
#| echo: false
library(tidyverse)
library(kableExtra)
library(knitr)
```

Here's your roadmap for the semester! Each week, follow the general process outlined below:

-   Enjoy the notes / text <i class="fas fa-book-open"></i>

-   Attend class, review the <i class="fas fa-pencil-alt"></i>warm-up and solutions if you have any questions after completing it during class.

-   Complete the HW assignment (<i class="fa-solid fa-file-pdf"></i> pdf & <i class="fa-brands fa-r-project"></i> Rmd linked below), <i class="fa-solid fa-paper-plane"></i> submit the assignment via Gradescope accessed on the course Canvas site.  <b>HW is due weekly on Wednesday at 11:59pm.</b>

-   Discuss the reflection questions <i class="fas fa-lightbulb" target="_blank"></i> and ethics considerations <i class="fas fa-balance-scale"></i> (see the <i class="fas fa-book-open"></i> class notes) with your classmates, mentor, and professor.

-   The textbook is **Practicing Statistics**, by Kuiper and Sklar.


```{r echo = FALSE}
schedule <- tribble(
  ~`date`, ~agenda, ~readings, ~homework, ~`handouts`, ~`warm-ups`,
  "Week 1 <br> 1.17.23", 
  '• t-tests + <br>• SLR',
  'Kuiper & Sklar: 2 <br> <a href="http://st47s.com/Math150/Notes/intro.html#intro" target = "_blank"><i class="fas fa-book-open"></i> introduction</a> <br> <a href="http://st47s.com/Math150/Notes/t-tests-vs-slr.html#ttest" target = "_blank"><i class="fas fa-book-open"></i> t-test</a> <br> <a href="http://st47s.com/Math150/Notes/t-tests-vs-slr.html#tslr" target = "_blank"><i class="fas fa-book-open"></i> t-test as SLR</a>', 
  '',
  '',
  '<a href="https://m150-method-biostat.netlify.app/handout/wu1_ma150_s23.pdf" target = "_blank"><i class="fas fa-pencil-alt"></i> WU 1</a> <br> <a href="https://m150-method-biostat.netlify.app/hw/wu2_ma150_s23.pdf" target = "_blank"><i class="fas fa-pencil-alt"></i> WU 2</a>',
  
"Week 2 <br> 1.24.23", 
  '• SLR <br> • contingency analysis',
  'Kuiper & Sklar: 2 & 6 <br> <a href="http://st47s.com/Math150/Notes/intro.html#slr" target = "_blank"><i class="fas fa-book-open"></i> SLR</a> <br> <a href="http://st47s.com/Math150/Notes/intro.html#fisher" target = "_blank"><i class="fas fa-book-open"></i> Fisher&#39;s Exact Test</a> <br> <a href="http://st47s.com/Math150/Notes/intro.html#catest" target = "_blank"><i class="fas fa-book-open"></i> categorical analysis</a>', 
  '<a href="https://m150-method-biostat.netlify.app/handout/MA150_HW1s23.pdf" target = "_blank"><i class="fa-solid fa-file-pdf"></i> HW1 pdf</a> <br> <a href="https://m150-method-biostat.netlify.app/handout/MA150_HW1s23.Rmd" target = "_blank"><i class="fa-brands fa-r-project"></i> HW1 Rmd</a> <br> <a href="https://canvas.pomona.edu/" target = "_blank"><i class="fa-solid fa-paper-plane"></i> HW1 turn-in</a>',
  '',
  '',

"Week 3 <br> 1.31.23",   
  '• contingency analysis',
  'Kuiper & Sklar: 6 <br> <a href="http://st47s.com/Math150/Notes/intro.html#studies" target = "_blank"><i class="fas fa-book-open"></i> types of studies</a> <br> <a href="http://st47s.com/Math150/Notes/intro.html#rr" target = "_blank"><i class="fas fa-book-open"></i> RR and CI</a> <br> <a href="http://st47s.com/Math150/Notes/intro.html#or" target = "_blank"><i class="fas fa-book-open"></i> OR and CI</a>',
  '',
  '',
  '',
  
"Week 4 <br> 2.7.23", 
  '• logistic regression',
  'Kuiper & Sklar: 7 <br> <a href="http://st47s.com/Math150/Notes/intro.html#logmodel" target = "_blank"><i class="fas fa-book-open"></i> logistic regression</a> <br> <a href="http://st47s.com/Math150/Notes/intro.html#logMLE" target = "_blank"><i class="fas fa-book-open"></i> MLE</a>',
  '',
  '',
  '',
  
  
"Week 5 <br> 2.14.23",
  '• logistic regression',
  'Kuiper & Sklar: 7 <br> <a href="http://st47s.com/Math150/Notes/intro.html#loging" target = "_blank"><i class="fas fa-book-open"></i> inference, logistic regression</a> <br> <a href="http://st47s.com/Math150/Notes/intro.html#logMLE" target = "_blank"><i class="fas fa-book-open"></i> multiple logistic regression</a>',
  '',
  '',
  '',
  
"Week 6 <br> 2.21.23", 
  '• logistic regression',
  'Kuiper & Sklar: 7 <br> <a href="http://st47s.com/Math150/Notes/intro.html#logstep" target = "_blank"><i class="fas fa-book-open"></i> model building</a> <br> <a href="http://st47s.com/Math150/Notes/intro.html#roc" target = "_blank"><i class="fas fa-book-open"></i> ROC</a>',
  '',
  '',
  '',

"Week 7 <br> 2.28.23", 
  '• modeling',
  '<a href="http://st47s.com/Math150/Notes/intro.html#cv" target = "_blank"><i class="fas fa-book-open"></i> cross validation</a> <br> <a href="http://st47s.com/Math150/Notes/intro.html#tidymodels" target = "_blank"><i class="fas fa-book-open"></i> `tidymodels`</a>',
  '',
  '',
  '',



'<font color = "#114B5F"><b>Week 8 <br> 3.7.23</b></font>', 
'<font color = "#114B5F"><b>review & catch-up</b></font>',
'<font color = "#114B5F"><b>exam 1 in class + <br> 3.9.23</b></font>',
 '',
  '<a href="https://canvas.pomona.edu/" target = "_blank"><i class="fa-solid fa-paper-plane"></i> see Canvas</a> for sample exam 1 Q & sol',
  '',

'<font color = "#114B5F">3.14.23</b></font>', '<font color = "#114B5F"><b>Spring Break</b></font>',"", 
  '',
  '',
  '',      

"Week 9 <br> 3.21.23", 
  '• survival analysis',
  'Kuiper & Sklar: 9 <br> <a href="http://st47s.com/Math150/Notes/intro.html#timedata" target = "_blank"><i class="fas fa-book-open"></i> time to event </a> <br> <a href="http://st47s.com/Math150/Notes/intro.html#KM" target = "_blank"><i class="fas fa-book-open"></i> KM curves</a> <br> <a href="http://st47s.com/Math150/Notes/intro.html#KMCI" target = "_blank"><i class="fas fa-book-open"></i> KM CI</a>',
  '',
  '',
  '', 
  
"Week 10 <br> 3.28.23", 
  '• survival analysis',
  'Kuiper & Sklar: 9 <br> <a href="http://st47s.com/Math150/Notes/intro.html#logrank" target = "_blank"><i class="fas fa-book-open"></i> log rank tests </a> <br> <a href="http://st47s.com/Math150/Notes/intro.html#hazfunc" target = "_blank"><i class="fas fa-book-open"></i> hazard functions</a>',
  '',
  '',
  '', 

"Week 11 <br> 4.4.23", 
  '• survival analysis',
  'Kuiper & Sklar: 9 <br> <a href="http://st47s.com/Math150/Notes/intro.html#coxph" target = "_blank"><i class="fas fa-book-open"></i> Cox PH model </a> <br> <a href="http://st47s.com/Math150/Notes/intro.html#multcoxph" target = "_blank"><i class="fas fa-book-open"></i> multiple Cox PH</a>',
  '',
  '',
  '', 
  
"Week 12 <br> 4.11.23", 
  '• survival analysis',
  'Kuiper & Sklar: 9 <br> <a href="http://st47s.com/Math150/Notes/intro.html#testingph" target = "_blank"><i class="fas fa-book-open"></i> assessing PH </a> <br> <a href="http://st47s.com/Math150/Notes/intro.html#Ioannidis" target = "_blank"><i class="fas fa-book-open"></i> most published research</a>',
  '',
  '',
  '',  


"Week 13 <br> 4.18.23", 
  '• multiple comparisons',
  '<a href="http://st47s.com/Math150/Notes/intro.html#multcomp" target = "_blank"><i class="fas fa-book-open"></i> multiple comparisons </a> <br> <a href="http://st47s.com/Math150/Notes/intro.html#qvals" target = "_blank"><i class="fas fa-book-open"></i> false discovery rate</a> <br> <a href="http://st47s.com/Math150/Notes/intro.html#interim" target = "_blank"><i class="fas fa-book-open"></i> interim analyses</a>',
  '',
  '',
  '',  

'<font color = "#114B5F"><b>Week 14 <br> 4.25.23</b></font>', 
'<font color = "#114B5F"><b>review & catch-up</b></font>',
'<font color = "#114B5F"><b>exam 2 in class + <br> 4.27.23</b></font>',
 '',
  '<a href="https://canvas.pomona.edu/" target = "_blank"><i class="fa-solid fa-paper-plane"></i> see Canvas</a> for sample exam 2 Q & sol',
  '',

"Week 15 <br> 5.2.23", 
  '• Poisson regression',
  '<a href="http://st47s.com/Math150/Notes/intro.html#regPois" target = "_blank"><i class="fas fa-book-open"></i> Poisson regression </a>',
  '',
  '',
  '',  
  
'<font color = "#114B5F"><b>Tuesday <br> 5.9.23 <br> 2-5pm</b></font>', '<font color = "#114B5F"><b>Final Project </b></font>',"", 
  '',
  '',
  ''   
  )
```


```{r}
#| echo: false
#| column: screen-inset
# can use column: page for the entire page
# can use column: body-outset to bleed outside the center column of text
schedule %>% 
  mutate_all(linebreak) %>% # required for linebreaks to work
  kbl(escape = FALSE, align = c(rep('l',6))) %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = TRUE) %>%
  column_spec(1:6,extra_css = "vertical-align:top;")
```




