---
title: "Schedule"
description: |
  Schedule for Math 150, Methods in Biostatistics, Spring 2025
execute: 
  message: false
  warning: false
---

```{r}
#| echo: false
library(tidyverse)
library(kableExtra)
library(knitr)
```

Here's your roadmap for the semester! Each week, follow the general process outlined below:

-   Enjoy the <i class="fas fa-book-open"></i> notes / text 

-   Attend class, review the <i class="fas fa-pencil-alt"></i> warm-up and solutions if you have any questions after completing it during class.
Read the weekly <i class="fas fa-newspaper"></i> article before class every Monday.

-   Complete the HW assignment (<i class="fa-solid fa-file-pdf"></i> pdf & qmd linked below), <i class="fa-solid fa-paper-plane"></i> submit the assignment via <i class="fa-brands fa-gradescope"></i> Gradescope from <i class="fa-brands fa-github"></i> GitHub accessed on the course Canvas site.  <b>HW is due weekly on Tuesday at 11:59pm.</b>

-   Homework assignments are found at the <a href = "https://github.com/orgs/ST47S-MethBio-Spring2025/repositories" target = "_blank"> <i class="fa-brands fa-github"></i> GitHub course organization</a>.  Due dates are provided on each assignment (roughly every other week).  See the <a href = "https://m150-method-biostat.netlify.app/github">course GitHub page</a> for more information on how to find, complete, and submit assignments.

-   There will be six in class quizzes.

-   The textbook is **Practicing Statistics**, by Kuiper and Sklar.


```{r}
#| echo: false

schedule <- tribble(
  ~`date`, ~agenda, ~readings, ~homework, ~`article (Mon)`, ~`worksheets`,
  "Week 1 <br> 1.22.25", 
  '• t-tests + <br>• SLR',
  'Kuiper & Sklar: 2 <br> <a href="http://st47s.com/Math150/Notes/intro.html#intro" target = "_blank"><i class="fas fa-book-open"></i> introduction</a> <br> <a href="http://st47s.com/Math150/Notes/t-tests-vs-slr.html#ttest" target = "_blank"><i class="fas fa-book-open"></i> t-test</a> <br> <a href="http://st47s.com/Math150/Notes/t-tests-vs-slr.html#tslr" target = "_blank"><i class="fas fa-book-open"></i> t-test as SLR</a>', 
  ' ',
  '<a href = "https://hardin47.github.io/CURV/scholars/benn.html" target = "_blank">Emma Benn</a>',
  '<a href="https://m150-method-biostat.netlify.app/handout/ws1_ma150_s25_notation.pdf" target = "_blank">{{< fa pencil >}} WS 1 - notation</a>',

"Week 2 <br> 1.27.25", 
  '• SLR <br> • contingency analysis',
  'Kuiper & Sklar: 2 & 6 <br> <a href="http://st47s.com/Math150/Notes/SLR.html#SLR" target = "_blank"><i class="fas fa-book-open"></i> SLR</a> <br> <a href="https://st47s.com/Math150/Notes/analysis-of-categorical-data.html#catest" target = "_blank"><i class="fas fa-book-open"></i> categorical analysis</a>', 
  '<a href="https://github.com/orgs/ST47S-MethBio-Spring2025/repositories" target = "_blank">{{< fa code >}} HW 1</a> - due 1.28.25',
  '<a href = "https://netflixtechblog.com/what-is-an-a-b-test-b08cc1b57962" target = "_blank"><i class="fas fa-newspaper"></i> A/B testing at Netflix</a> <br> <br> <a href = "https://hardin47.github.io/CURV/scholars/irizarry.html" target = "_blank">Rafael Irizarry</a>',
  '<a href="https://m150-method-biostat.netlify.app/handout/ws2_ma150_s25_CI.pdf" target = "_blank">{{< fa pencil >}} WS 2 - CIs</a> <br> <a href="https://m150-method-biostat.netlify.app/handout/ws3_ma150_s25_cond.pdf" target = "_blank">{{< fa pencil >}} WS 3 - tech conds</a>',

"Week 3 <br> 2.3.25",   
  '• contingency analysis',
  'Kuiper & Sklar: 6 <br> <a href="https://st47s.com/Math150/Notes/analysis-of-categorical-data.html#studies" target = "_blank"><i class="fas fa-book-open"></i> types of studies</a> <br> <a href="https://st47s.com/Math150/Notes/analysis-of-categorical-data.html#rr" target = "_blank"><i class="fas fa-book-open"></i> RR and CI</a> <br> <a href="https://st47s.com/Math150/Notes/analysis-of-categorical-data.html#or" target = "_blank"><i class="fas fa-book-open"></i> OR and CI</a>',
  '<a href="https://github.com/orgs/ST47S-MethBio-Spring2025/repositories" target = "_blank">{{< fa code >}} HW 2</a> - due 2.4.25 <br> <i class="fa-solid fa-clipboard-question"></i> Quiz 1 on 2.5.25',
  '<a href = "https://www.nytimes.com/2020/12/13/learning/what-does-95-effective-mean-teaching-the-math-of-vaccine-efficacy.html" target = "_blank"><i class="fas fa-newspaper"></i> what is efficacy?</a> <br> <a href = "https://www.nytimes.com/2020/11/18/health/pfizer-covid-vaccine.html" target = "_blank"><i class="fas fa-newspaper"></i> efficacy</a> <br> <br> <a href = "https://hardin47.github.io/CURV/scholars/small-rodriguez.html" target = "_blank">Desi Small-Rodriguez</a>',
  '<a href="https://m150-method-biostat.netlify.app/handout/ws4_ma150_s25_botox.pdf" target = "_blank">{{< fa pencil >}} WS 4 - sampling distributions</a>',
  
"Week 4 <br> 2.10.25", 
  '• logistic regression',
  'Kuiper & Sklar: 7 <br> <a href="https://st47s.com/Math150/Notes/logreg.html#the-logistic-model" target = "_blank"><i class="fas fa-book-open"></i> logistic regression</a> <br> <a href="https://st47s.com/Math150/Notes/logreg.html#logMLE" target = "_blank"><i class="fas fa-book-open"></i> MLE</a>',
  '<a href="https://github.com/orgs/ST47S-MethBio-Spring2025/repositories" target = "_blank">{{< fa code >}} HW 3</a> - due 2.11.25 ',
  '<a href = "https://www.nytimes.com/2014/02/26/health/obesity-rate-for-young-children-plummets-43-in-a-decade.html" target = "_blank"><i class="fas fa-newspaper"></i> Obesity in Children Plummets</a> <br> <a href = "https://jamanetwork.com/journals/jama/fullarticle/1832542" target = "_blank"><i class="fas fa-newspaper"></i> JAMA article here (see Table 6)</a> <br> <a href = "https://www.nytimes.com/2020/04/17/parenting/growth-chart-accuracy.html" target = "_blank"><i class="fas fa-newspaper"></i> growth curves</a> <br> <br> <a href = "https://hardin47.github.io/CURV/scholars/santos.html" target = "_blank">Robert Santos</a>',
  '<a href="https://m150-method-biostat.netlify.app/handout/ws5_ma150_s25_glms.pdf" target = "_blank">{{< fa pencil >}} WS 5 - log-linear model</a> <br> <a href="https://m150-method-biostat.netlify.app/handout/ws6_ma150_s25_mle.pdf" target = "_blank">{{< fa pencil >}} WS 6 - MLE</a>',
  
  
"Week 5 <br> 2.17.25",
  '• logistic regression',
  'Kuiper & Sklar: 7 <br> <a href="https://st47s.com/Math150/Notes/logreg.html#loginf" target = "_blank"><i class="fas fa-book-open"></i> inference, logistic regression</a> <br> <a href="https://st47s.com/Math150/Notes/logreg.html#multlog" target = "_blank"><i class="fas fa-book-open"></i> multiple logistic regression</a>',
  '<a href="https://github.com/orgs/ST47S-MethBio-Spring2025/repositories" target = "_blank">{{< fa code >}} HW 4</a> - due 2.18.25 <br> <i class="fa-solid fa-clipboard-question"></i> Quiz 2 on 2.19.25',
  '<a href = "https://weallcount.com/2019/06/21/intersectionality-data-2/" target = "_blank"><i class="fas fa-newspaper"></i> intersectional data</a> <br> <br> <a href = "https://hardin47.github.io/CURV/scholars/rosenbluth.html" target = "_blank">Arianna Wright Rosenbluth</a>',
    '<a href="https://m150-method-biostat.netlify.app/handout/ws7_ma150_s25_interaction.pdf" target = "_blank">{{< fa pencil >}} WS 7 - interaction</a>',
  
"Week 6 <br> 2.24.25", 
  '• logistic regression',
  'Kuiper & Sklar: 7 <br> <a href="http://st47s.com/Math150/Notes/process.html" target = "_blank"><i class="fas fa-book-open"></i> model process</a> <br> <a href="http://st47s.com/Math150/Notes/process.html#cross-validation" target = "_blank"><i class="fas fa-book-open"></i> cross validation</a> <br> <a href="https://st47s.com/Math150/Notes/logreg.html#roc" target = "_blank"><i class="fas fa-book-open"></i> ROC</a>',
  '<a href="https://github.com/orgs/ST47S-MethBio-Spring2025/repositories" target = "_blank">{{< fa code >}} HW 5</a> - due 2.25.25 ',
  '<a href = "https://journals.sagepub.com/doi/10.1177/2515245917747646" target = "_blank"><i class="fas fa-newspaper"></i> many models <br> (Tables 3 & 4, Fig 2)</a>  <br> <br> <a href = "https://hardin47.github.io/CURV/scholars/bowman.html" target = "_blank">DuBois Boman</a>',
  '<a href="https://m150-method-biostat.netlify.app/handout/ws8_ma150_s25_lrt.pdf" target = "_blank">{{< fa pencil >}} WS 8 - drop-in-deviance test </a> <br> <br> <a href="https://m150-method-biostat.netlify.app/handout/ws9_ma150_s25_cv.pdf" target = "_blank">{{< fa pencil >}} WS 9 - cross validation </a> <br> <br>  <br> <br> <a href="https://m150-method-biostat.netlify.app/handout/2025-02-26-tidymodels.html" target = "_blank"><i class="fas fa-desktop"></i> tidymodels</a> <br> <a href="https://m150-method-biostat.netlify.app/handout/simppar_log.pdf" target = "_blank"><i class="fas fa-pencil-alt"></i> Simpson&#39;s Paradox</a> ',

"Week 7 <br> 3.3.25", 
  '• modeling',
  '<a href=  "https://st47s.com/Math150/Notes/logreg.html#logstep" target = "_blank"><i class="fas fa-book-open"></i> model building</a> ',
  '<a href="https://github.com/orgs/ST47S-MethBio-Spring2025/repositories" target = "_blank">{{< fa code >}} HW 6</a> - due 3.4.25 <br> <i class="fa-solid fa-clipboard-question"></i> Quiz 3 on 3.5.25',
  '<a href = "https://www.kff.org/policy-watch/a-look-at-federal-health-data-taken-offline/" target = "_blank"><i class="fas fa-newspaper"></i> health data taken offline</a>  <br> <br> <a href = "https://hardin47.github.io/CURV/scholars/hughes-oliver.html" target = "_blank">Jacqueline Hughes-Oliver</a>',
  '<a href="https://m150-method-biostat.netlify.app/handout/ws9_ma150_s25_cv.pdf" target = "_blank">{{< fa pencil >}} WS 9 - cross validation </a> <br> <br><br> <br> <a href="https://m150-method-biostat.netlify.app/handout/2025-03-03-ROC-onestep.html" target = "_blank"><i class="fas fa-desktop"></i> ROC + one variable building</a> <br> <a href="https://m150-method-biostat.netlify.app/handout/variables.pdf" target = "_blank"><i class="fas fa-pencil-alt"></i>variable handout</a>',


"Week 8 <br> 3.10.25", 
  '• survival analysis',
  'Kuiper & Sklar: 9 <br> <a href="https://st47s.com/Math150/Notes/survival-analysis.html#timedata" target = "_blank"><i class="fas fa-book-open"></i> time to event </a> <br> <a href="https://st47s.com/Math150/Notes/survival-analysis.html#KM" target = "_blank"><i class="fas fa-book-open"></i> KM curves</a> ',
  ' ',
  '<a href = "https://jamanetwork.com/journals/jamanetworkopen/fullarticle/2799017" target = "_blank"><i class="fas fa-newspaper"></i> placebo effect (read abstract and Fig 3)</a> <br> <br>  <a href = "https://hardin47.github.io/CURV/scholars/nuzzo.html" target = "_blank">Regina Nuzzo</a>',
  ' ', 

"3.17.25", '• Spring Break', ' ', ' ', ' ', ' ',
  

"Week 9 <br> 3.24.25", 
  '• survival analysis',
  'Kuiper & Sklar: 9 <br> <a href="https://st47s.com/Math150/Notes/survival-analysis.html#KM" target = "_blank"><i class="fas fa-book-open"></i> KM curves</a> <br> <a href="https://st47s.com/Math150/Notes/survival-analysis.html#KMCI" target = "_blank"><i class="fas fa-book-open"></i> KM CI</a>',
  '<a href="https://github.com/orgs/ST47S-MethBio-Spring2025/repositories" target = "_blank">{{< fa code >}} HW 7</a> - due 3.25.25 ',
  '<a href = "https://www.nature.com/articles/d41586-023-00030-3" target = "_blank"><i class="fas fa-newspaper"></i> Alzheimer&#39;s</a> <br> <br> <a href = "https://hardin47.github.io/CURV/scholars/.html" target = "_blank"></a>',
  ' ', 


"Week 10 <br> 3.31.25", 
  '• survival analysis',
  'Kuiper & Sklar: 9 <br> <a href="https://st47s.com/Math150/Notes/survival-analysis.html#logrank" target = "_blank"><i class="fas fa-book-open"></i> log rank tests </a> <br> <a href="https://st47s.com/Math150/Notes/survival-analysis.html#hazfunc" target = "_blank"><i class="fas fa-book-open"></i> hazard functions</a>',
  '<a href="https://github.com/orgs/ST47S-MethBio-Spring2025/repositories" target = "_blank">{{< fa code >}} HW 8</a> - due 4.1.25 <br> <i class="fa-solid fa-clipboard-question"></i> Quiz 4 on 4.2.25',
  '<a href = "https://www.sciencedirect.com/science/article/pii/S000291652366280X?via%3Dihub" target = "_blank"><i class="fas fa-newspaper"></i> the million veteran program</a> <br> <br> <a href = "https://hardin47.github.io/CURV/scholars/.html" target = "_blank"></a>',
  '  ', 

"Week 11 <br> 4.7.25", 
  '• survival analysis',
  'Kuiper & Sklar: 9 <br> <a href="https://st47s.com/Math150/Notes/survival-analysis.html#coxph" target = "_blank"><i class="fas fa-book-open"></i> Cox PH model </a> <br> <a href="https://st47s.com/Math150/Notes/survival-analysis.html#multcoxph" target = "_blank"><i class="fas fa-book-open"></i> multiple Cox PH</a>',
  '<a href="https://github.com/orgs/ST47S-MethBio-Spring2025/repositories" target = "_blank">{{< fa code >}} HW 9</a> - due 4.8.25',
  '<a href = "https://www.thelancet.com/journals/lancet/article/PIIS0140-6736(2032076-6/fulltext" target = "_blank"><i class="fas fa-newspaper"></i> race-conscious medicine</a> <br> <br> <a href = "https://hardin47.github.io/CURV/scholars/.html" target = "_blank"></a>',
  '  <br> <br> <a href="https://m150-method-biostat.netlify.app/handout/CHD_HR.pdf" target = "_blank"><i class="fas fa-pencil-alt"></i>CHD & HR</a>',
  
"Week 12 <br> 4.14.25", 
  '• survival analysis',
  'Kuiper & Sklar: 9 <br> <a href="https://st47s.com/Math150/Notes/survival-analysis.html#testingph" target = "_blank"><i class="fas fa-book-open"></i> assessing PH </a> <br> <a href="https://st47s.com/Math150/Notes/multiple-comparisons.html#Ioannidis" target = "_blank"><i class="fas fa-book-open"></i> most published research</a>',
  '<a href="https://github.com/orgs/ST47S-MethBio-Spring2025/repositories" target = "_blank">{{< fa code >}} HW 10</a> - due 4.15.25 <br> <i class="fa-solid fa-clipboard-question"></i> Quiz 5 on 4.16.25',
  '<a href = "https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.0020124" target = "_blank"><i class="fas fa-newspaper"></i> most published research</a> <br> <a href = "https://replicationindex.com/2020/12/24/ioannidis-is-wrong/" target = "_blank"><i class="fas fa-newspaper"></i> science problems</a> <br> <br> <a href = "https://twitter.com/GidMK/status/1376304539897237508?s=20" target = "_blank">abuse of power</a> <br> <br> <a href = "https://hardin47.github.io/CURV/scholars/.html" target = "_blank"></a>',
  ' ',  


"Week 13 <br> 4.21.25", 
  '• multiple comparisons',
  '<a href="https://st47s.com/Math150/Notes/multiple-comparisons.html#multcomp" target = "_blank"><i class="fas fa-book-open"></i> multiple comparisons </a> <br> <a href="https://st47s.com/Math150/Notes/multiple-comparisons.html#qvals" target = "_blank"><i class="fas fa-book-open"></i> false discovery rate</a> <br> <a href="https://st47s.com/Math150/Notes/multiple-comparisons.html#interim" target = "_blank"><i class="fas fa-book-open"></i> interim analyses</a>',
  '<a href="https://github.com/orgs/ST47S-MethBio-Spring2025/repositories" target = "_blank">{{< fa code >}} HW 11</a> - due 4.22.25 <br> <font color = "#114B5F"><b><a href = "https://m150-method-biostat.netlify.app/project.html" target = "_blank"><i class="fa-solid fa-list-check"></i> Project: EDA</a></b></font> due 4.23.25',
  '<a href = "https://www.nytimes.com/2020/10/14/health/covid-clinical-trials.html" target = "_blank"><i class="fas fa-newspaper"></i> pausing trials</a> <br> <br> <a href = "https://hardin47.github.io/CURV/scholars/.html" target = "_blank"></a> ',
  ' ',  

"Week 14 <br> 4.28.25", 
  '• multiple comparisons',
  '<a href="https://st47s.com/Math150/Notes/multiple-comparisons.html#multcomp" target = "_blank"><i class="fas fa-book-open"></i> multiple comparisons </a> <br> <a href="https://st47s.com/Math150/Notes/multiple-comparisons.html#qvals" target = "_blank"><i class="fas fa-book-open"></i> false discovery rate</a> <br> <a href="https://st47s.com/Math150/Notes/multiple-comparisons.html#interim" target = "_blank"><i class="fas fa-book-open"></i> interim analyses</a>',
  '<a href="https://github.com/orgs/ST47S-MethBio-Spring2025/repositories" target = "_blank">{{< fa code >}} HW 12</a> - due 4.29.25 <br> <i class="fa-solid fa-clipboard-question"></i> Quiz 6 on 4.30.25',
  '<a href = "" target = "_blank"><i class="fas fa-newspaper"></i> </a> <a href = "https://towardsdatascience.com/missing-data-effects-on-the-correlation-between-ice-cream-sales-and-temperature-f4bb2b3fcde1" target = "_blank"><i class="fas fa-newspaper"></i> missing data</a> <br> <br> <a href = "https://hardin47.github.io/CURV/scholars/.html" target = "_blank"></a>  ',
  ' ', 

"Week 15 <br> 5.5.25", 
  ' ',
  ' ',
'<font color = "#114B5F"><b><a href = "https://m150-method-biostat.netlify.app/project.html" target = "_blank"> <i class="fa-solid fa-list-check"></i> Project: Graphic</a></b></font> in class 5.7.25',
  ' ',
  ' ',

"Week 16 <br> 5.16.25", 
  ' ',
  ' ',
'<font color = "#114B5F"><b><a href = "https://m150-method-biostat.netlify.app/project.html" target = "_blank"> <i class="fa-solid fa-list-check"></i> Project: Final</a></b></font> due 5.16.25',
  ' ',
  ' '
  )
```


```{r}
#| echo: false
#| column: screen-inset
# can also use column: screen-inset also the entire page??
# can use column: page for the entire page
# can use column: body-outset to bleed outside the center column of text
schedule |> 
  gt::gt() |> 
  gt::fmt_markdown(columns = everything()) |> 
    gt::cols_width(date ~ pct(8),
                   agenda ~ pct(12),
                   everything() ~ pct(20)) 
```




