---
title: "Variables: one at a time"
subtitle: "Math 150 - Spring 2025"
format: pdf
---

```{r}
#| include: false

# figure options
knitr::opts_chunk$set(warning = FALSE, message = FALSE,
  fig.width = 10, fig.asp = 0.618, out.width = "90%",
  fig.retina = 3, dpi = 300, fig.align = "center"
)

library(tidyverse)
library(tidymodels)
library(broom)
```

#### More metrics

* AIC: Akaike's Information Criteria = $-2\ln L + 2p$

* BIC: Bayesian Information Criteria = $-2 \ln L + p \ln(n)$

> choose a model with the smallest AIC or BIC (i.e., the biggest likelihood)

#### Variable Selection

> Forward: start with the "best" variable and add variables one at a time

> Backward: start with the full model and remove variables one at a time

> Best: find the "best" combo of variables (check them all!) for a specified number of variables

#### Tools

* **tidymodels** does not make it easy to add or drop 1 variable at a time.

* `add1()` and `drop1()` functions do not make it easy to work with dozens of predictors and missing data.

Therefore, we'll go back to the bird data from HW 5.

```{r}
#| echo: false

nests <- readr::read_csv("./data/C7 Birdnest.csv", na="*") %>%
  drop_na() %>%
  mutate(Location = case_when(
    Location == "bridge" ~ "wall",
    Location == "building" ~ "wall",
    Location == "cliff" ~ "wall",
    TRUE ~ Location
  )) 
```

```{r}
nests %>% select(Location) %>% table()
```


#### Forward +1

```{r}
#| echo: true

glm(`Closed?` ~ 1, data = nests, family="binomial") %>%
  add1(scope = ~ Length + Location + No.eggs + Color +
         Incubate + Nestling + Totcare, test = "Chisq")
```

#### Forward +2

```{r}
#| echo: true

glm(`Closed?` ~ Location, data = nests, family="binomial") %>%
  add1(scope = ~ Length + Location + No.eggs + Color +
         Incubate + Nestling + Totcare, test = "Chisq")
```


#### Forward +3

```{r}
#| echo: true

glm(`Closed?` ~ No.eggs + Location, data = nests, family="binomial") %>%
  add1(scope = ~ Length + Location + No.eggs + Color +
         Incubate + Nestling + Totcare, test = "Chisq")
```


#### Backward -1 

```{r}
#| echo: true

glm(`Closed?` ~ Length + Location + No.eggs + Color +
         Incubate + Nestling + Totcare, data = nests, family="binomial") %>%
  drop1(test = "Chisq")
```

#### Backward -2 

```{r}
#| echo: true

glm(`Closed?` ~ Length + Location + No.eggs + Color +
         Incubate  + Totcare, data = nests, family="binomial") %>%
  drop1(test = "Chisq")
```

#### Backward -2 

```{r}
#| echo: true

glm(`Closed?` ~ Length + Location + No.eggs + Incubate  + Totcare, 
    data = nests, family="binomial") %>%
  drop1(test = "Chisq")
```


#### Backward -3 

```{r}
#| echo: true

glm(`Closed?` ~ Length + Location + No.eggs + Totcare, 
    data = nests, family="binomial") %>%
  drop1(test = "Chisq")
```



#### Automatic: Forward w AIC

```{r}
#| echo: true

glm(`Closed?` ~ 1, data = nests, family="binomial") %>%
  stats::step(scope = ~ Length + Location + No.eggs + Color +
         Incubate + Nestling + Totcare, 
         direction = "forward", k = 2)

```

#### Final Forward AIC

```{r}
#| echo: true

glm(`Closed?` ~ Length + Location + No.eggs + Nestling,
    data = nests, family="binomial") %>% tidy()
```


#### Automatic: Backward w BIC

```{r}
#| echo: true

glm(`Closed?` ~ Length + Location + No.eggs + Color +
         Incubate + Nestling + Totcare,
    data = nests, family="binomial") %>%
  stats::step(scope = ~ Length + Location + No.eggs + Color +
         Incubate + Nestling + Totcare, 
         direction = "backward", k = log(86))

```


#### Final Backward BIC

```{r}
#| echo: true

glm(`Closed?` ~ Length + No.eggs + Nestling,
    data = nests, family="binomial") %>% tidy()
```


